---
format: 
  html: 
    toc: true
    theme: "flatly"
---

```{r, packages_data_fns}
#| echo: false
#| include: false

#load packages
source("0_set_up.R")

#import data
aa_data <- import("data/aa_data_wide_nogeo_2023.rds", trust=TRUE)

```

```{r, r_objs_vic}
#| include: false
#| echo: false

injur_tot <- aa_data |> 
  drop_na(c(wound_tot,kill_tot)) |> 
  mutate(injur_tot = wound_tot+kill_tot) |> 
  summarise(injur_tot = sum(injur_tot)) |> 
  pull(injur_tot) 

kill_tot <- aa_data |> 
  drop_na(kill_tot) |> 
  summarise(kill_tot = sum(kill_tot)) |> 
  pull(kill_tot)

wound_tot <- aa_data |> 
  drop_na(wound_tot) |> 
  summarise(wound_tot = sum(wound_tot)) |> 
  pull(wound_tot)

```

## We Remember

Between 2000 and `{r} max(aa_data$year, na.rm=TRUE)`, our nation has 
experienced `{r} nrow(aa_data)` active attack events. There were a total of 
`{r} format_num(injur_tot)` people injured, and out of that number, 
`{r} format_num(kill_tot)` 
people died. This page attempts to list every name of every victim. Please 
alert us if any mistakes or omissions are found. We attempt to capture every 
name we can find to remember the victims.  

Let us pause for a moment of silence to remember and honor those lost. ALERRT 
also strives to honor with courage and compassion the thousands of surviving 
families and those who risked their lives to save others. 


{{< video www/victim_scroll.mp4 >}}

{{< downloadthis www/victim_scroll.mp4 dname="aa_victims" >}}

## Don't Name Them

At ALERRT, it is our policy to refrain from naming the person(s) 
responsible for active attacks. Research has shown that many attacks are the 
result of fame-seeking behavior by the attackers. By refusing to name them, we 
aim to remove fame and notoriety as possible motivators of future attacks. 
ALERRT hosts a website, [DontNameThem.org](dontnamethem.org), that provides 
more information and resources about the "Don't Name Them" movement. 







